Coeficientes para la corrección de bias

### 2021-07-27 analysis/chapters/coeficientes.Rmd
Revisión de epigrafes

```{r}
files <- list.files("/home/paola.corrales/datosmunin/EXP/E7-training/ANA", 
                    pattern = "asim.", recursive = TRUE, 
                    full.names = TRUE)
files <- files[!str_detect(files, pattern = "conv")]

>>>>

```{r}
files <- list.files("/home/paola.corrales/datosmunin3/EXP/E7-training/ANA", 
                    pattern = "asim.", recursive = TRUE, 
                    full.names = TRUE)
files <- files[!str_detect(files, pattern = "conv")]
